### 2014-04-30 paper.tex

The WPI-CMU team performed quite well for the period of 4 months. There are still a lot of research left to be performed, and a lot of improvements to be performed in the code base. The work put into the challenge were very task-specific to the specifications given by DARPA, and would probably perform poorly compared to anything else.

There is already research on all kind of algorithms, but for future years the problem will become more on how to put all of these pieces of work together under one platform, and allow the robot to autonomously perform operations on the world.

Boston Dynamics has giving news that the Atlas robot may change over time, and this provides further complications on how to adapt the current code to also take into account the additional changes without breaking the current features.

\section{Robust Dynamic Programming}
Model based optimal control is a powerful tool but relies heavily on the accuracy of the system model, which is not a trivial task to derive. There are many parameters involved, such as friction, sensor readings, calibrations, and the model may change over time due to wear, temperature, humidity, contact condition, and others.

>>>>

\chapter{Robust Dynamic Programming}
Model based optimal control is a powerful tool but relies heavily on the accuracy of the system model, which is not a trivial task to derive. There are many parameters involved, such as friction, sensor readings, calibrations, and the model may change over time due to wear, temperature, humidity, contact condition, and others.
